---
title: "A plan to maintain and increase my knowledge this year"
subtitle: "Focused on comprehensive exam preparation, but generally applicable to professional growth"
date: "Outlined 2021-03-17; last compiled `r Sys.Date()`"
output: 
  html_document:
    keep_md: false
---

```{r setup, include=F}
knitr::opts_chunk$set(
  message = F,
  warning = F,
  error = F,
  echo = F,
  fig.align = 'center',
  out.width = "95%"
)
knitr::opts_knit$set(root.dir = getwd())
```

## Summary

- I want to gradually chunk out some study time for reviewing the topics covered in the classes I took from my committee members.

- This will help prepare me for my comprehensive exam and also generally maintain my knowledge about these topics. 

- I also need to continue reading papers and learning skills

- Structuring time for these activities ensures they will get done.

- I will study each Monday morning for one hour, preferably between 9 and 10 AM. 

- I will read journal papers for one hour each Tuesday morning, preferably between 9 and 10 AM. 

- I will learn/practice computing skills for one hour each Wednesday morning, preferably between 9 and 10 AM. 

- The schedule is outlined below.


```{r study-plan, child='study-plan_2021-03-17.Rmd'}

```




```{r learning-plan, child='stuff-to-learn-March-2021.Rmd'}

```


